Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-12 providence/sections/intro.tex
added model. worked more on intro.

An audit will either end with a declaration that an election outcome is correct, or escalate to a full hand count. It may be evaluated based on how it deals with incorrect election outcomes, as the purpose is to detect these. A {\em risk-limiting audit (RLA)} guarantees a minimum probability of a full hand count if the election outcome is incorrect; this is the probability of correct functioning of the audit. Equivalently, an RLA guarantees a maximum probability of audit error if the election outcome is incorrect. This error measure is termed the {\em risk limit}, more rigorously defined as the maximum probability with which the audit would declare an incorrect election outcome as being correct.

@@

\subsection{Background on RLAs}
We provide here the background necessary to evaluate our contributions.

All RLAs sample one or more ballots at random; we will refer to each such set of ballots as a {\em round}. The ballots are manually examined, and a stopping condition computed, which determines whether (a) the audit ends in success (the election outcome is declared correct) or (b) another round should be drawn (more information is needed before a determination). In principle, the stopping condition could indicate a third option too: (c) the audit proceeds to a full manual hand count. However, a manual hand count presents significant logistical challenges, and there is always a chance that it will have been unnecessary, hence (c) is generally not incorporated. Election officials would typically decide to perform a full manual hand count if the audit does not stop in spite of drawing a large number of ballots, typically over multiple rounds. They would be influenced by the certification deadline, the estimated number of human hours required for another round, the logistical costs of a full hand count, and the impact of any decision on citizen confidence.

\subsubsection{Types of RLAs}
In a ballot comparison RLA \cite{RLA}, the manual interpretation of each sampled ballot is compared to the corresponding Cast Vote Record (CVR), which is the machine interpretation of the ballot. Ballot comparison RLAs require the fewest ballots of all known RLA approaches, but also require a means of identifying the CVR corresponding to a particular ballot. A typical approach is to use a ballot serial number on both paper ballot and CVR. When voters vote in precincts, however, serial numbers on ballots can enable the correlation of ballots with voters, and ballots are typically not numbered. Additionally, some voting systems do not record a CVR. One may perform a transitive audit by rescanning unnumbered voted ballots with special scanners which produce CVRs and also print numbers on the ballots as they are scanned. This requires an investment in a sufficiently large number of such printers and in the human effort of rescanning ballots, and is not always feasible.

In a ballot polling RLA \cite{RLA}, the manual interpretations of the sampled ballots are simply tallied. Ballot polling RLAs require a much larger number of ballots than ballot comparison RLAs, but are more feasible because they do not require any additional functionality of the voting system, and, in particular, do not need CVRs. What is needed is a complete ballot manifest (a list of ballot storage containers and the number of ballots in each) which enables the creation of a well defined list of the ballots and their locations (the fifth ballot in box number 20, for example).

A batch comparison RLA \cite{RI-report} samples batches of ballots (typically, a batch is a storage box of ballots) and compares the manual tally of each sampled batch with the announced tally of that batch. Thus, while this type of audit does not need CVRs, it does need both a ballot manifest and a public declaration of the tally of each batch. This approach typically requires the sampling of a very large number of ballots. However, the process is most similar to that which election officials already use when they perform fixed-percentage post-election audits, where, for example, 2\% of the batches are manually tallied. (Note that, for an RLA, the number of batches tallied is not fixed; the risk limit is. A smaller number of batches might be sufficient, or a larger number necessary, for an audit with the required risk limit.)

This paper focuses on ballot polling RLAs which have been used in a number of US state pilots (California, Georgia, Indiana, Michigan, Ohio, Pennsylvania, Virginia and elsewhere) and in real statewide audits (Georgia, Virgina) \cite{vv_audits} as well as in audits of smaller jurisdictions, such as Montgomery County, Ohio \cite{usenix_minerva}.

\subsubsection{Ballot Polling Audits}
Ballot polling audits proceed as follows. 
\begin{enumerate}
\item A first round \cite{usenix_minerva} size---the number of ballots sampled before first checking the stopping condition---is chosen. 
\item Ballots on the ballot manifest are sampled uniformly at random using a pseudorandom number generator typically seeded by a natural source of randomness like rolling dice.
\item The physical ballots are found and manually interpreted, recording the manual interpretations. 
\item Based on the manual interpretations, the stopping condition is computed. 
\item If more ballots are to be drawn, the next round size is chosen. Round sizes, including the first one, may be computed based on a desired probability of audit completion at the end of the round, and may take into consideration loose estimates of the resources required. For RLAs required by statute or law, certification deadlines would play a large role, as the audit would need to be completed before the deadline. 
\end{enumerate}

@@

Election officials typically draw ballots in large round sizes:  see for example \cite{va-2022,RI-report}, and note that, in addition to allowing users to directly enter a round size, Arlo provides choices of stopping probabilities of $0.9$, $0.8$ and $0.7$, and the expected number of ballots required by \BRAVO. Further, at both audits we attended, election officials chose stopping probabilities of $0.9$ and we are not aware of any ballot polling RLA performed on ballots cast in a governmental election that drew ballots one at a time (though the stopping condition can be computed one ballot at a time, the ballots are drawn in rounds). \BRAVO hence cannot be used as a B2 audit in these scenarios.

@@

\subsubsection{Adversarial Model for RLAs}
Detailed descriptions of best practices for post-election audits may be found in \cite{best-practices,why-and-how}. For our purposes, we will assume that the best practices are followed: the paper trail consists of hand-marked paper ballots and is secured; a public compliance audit is carried out before the RLA to ensure that the processes for securing the paper trail were followed; voter authentication and registration processes were verified, and only legitimate voters cast no more than a single vote each; the risk-limiting audit is public. We will further assume that all software used in the RLA is open source and well-defined, so its output may be reproduced and thus verified by an observer wishing to do so with their own software.

Referring to the ballot polling audit steps described above, we further assume that a secure PRNG is used; the seed is generated uniformly at random in a public process; the process of locating ballots is publicly observable and the located ballots can be viewed by the public. Because the PRNG is well-defined, as is the stopping condition, we may assume that the stopping condition is correctly computed from knowledge of the seed and the drawn ballots. Thus the only variable is round size. We define a {\em weak adversary} as one who can choose the first round size and a {\em strong adversary} as one who can choose any round size.

\subsection{The Literature and Open Questions}
Zag\'{o}rski {\em et al.} propose ballot polling RLA \Minerva \cite{usenix_minerva}, which does not need ballot order and relies only on sample and round tallies. They prove that it is risk-limiting when the number of relevant ballots drawn in each round is pre-determined before any ballots are examined; that is, for a weak adversary. They do not address the case of a strong adversary (such as an audit insider) who can determine the size of the next round after knowing what votes are on the ballots sampled thus far. In particular, an open question about \Minerva is whether the computation of a risk limit assuming a weak adversary applies to an attack by a strong adversary, or is the risk limit computation incorrect when the adversary is strong? Can the strong adversary increase the audit's error probability beyond its declared risk limit? Or is there no probabilistic adversarial advantage to being able to compute next round sizes after knowing the drawn sample? We do not answer this question, and to our knowledge, it remains open.

@@

A major limitation of our understanding of the ballot polling problem as a community is that we use the number of ballots drawn or values proportional to this number \cite{mclaughlin_thesis,bernhard-diss,RI-report} as measures of the workload of an audit. If this were a correct measure of the workload of an audit, we would want to use B2 audits (round size is one) and make decisions about stopping the audit after drawing each ballot, because this leads to the smallest expected number of ballots. As described above, election officials, on the other hand, greatly prefer drawing many ballots at once. This preference is likely due to the following. 
\begin{description}
\item Firstly, each round has an overhead workload as well, including setting up the round and communicating among the various localities involved in conducting the audit (for example, audits of statewide contests involve the drawing of ballots at county offices where the ballots are stored). 
\item Secondly, there is an overhead to finding a storage box and unsealing it. For large round sizes, multiple ballots may be drawn at once from a box, and the number of boxes retrieved is smaller than the number of ballots (storage boxes commonly contain many hundreds of ballots each). For smaller round sizes, the number of times a box is retrieved would be roughly identical to the number of ballots drawn, as it is unlikely that a single box will hold multiple ballots from the sample. 
\item Finally, in the current environment of misinformation, election officials would want to ensure that the probability of a misleading audit sample (falsely indicating that the loser won) is very small, which implies that round sizes should be large. 
\end{description}
Thus the workload of an audit is not simply a linear (or affine) function of the number of ballots drawn. Relatedly, an optimal round schedule is not completely determined by the expected number of ballots drawn. It depends on other variables as well. The consideration of all these variables is necessary while planning an audit.

\subsection{Our Contributions}
Our primary contribution is a new RLA, \Providence, which gives the efficiency of \Minerva and is also resistant to a strong adversary. The stopping condition for \Minerva does not take into account the sample obtained in previous rounds, and, in \cite{usenix_minerva}, its risk limit is estimated through weighted averages across multiple rounds, assuming that round sizes do not depend on the previous sample. We are able to derive a new stopping condition for which a far simpler proof of the risk-limiting property is possible. In particular, this proof does not require an assumption about round sizes. We provide the following:
\begin{enumerate}
\item Proof that \Providence is an RLA and resistant to a strong adversary.
\item Simulations of \Providence, \Minerva, SO \BRAVO, and EoR \BRAVO which show that \Providence uses number of ballots similar to those of \Minerva, both fewer than either version of \BRAVO.
\item Results and analysis from the use of \Providence in a pilot audit in Rhode Island.
\item A model of workload that includes the overhead effort of each round and the overhead effort of retrieving a storage unit of ballots; simulations that illustrate the use of this model to compare the different types of ballot polling audits and to plan an audit with minimal workload.
\item An analysis of round size as a function of the maximum acceptable probability of a misleading audit sample.
\item Open source implementation of \Providence and audit planning tools. 
%including the novel metric Probability of Misleading(name?)
\end{enumerate}

@@

\subsection{Organization} 
Section \ref{sec:related} describes related work. Section \ref{sec:prov} describes the \Providence audit, Section \ref{sec:sims} the simulations comparing the number of ballots drawn using various ballot polling audits and section \ref{sec:pilot} the use of \Providence in an audit carried out by the Board of Elections of Rhode Island. Section \ref{sec:workload} presents our workload model and describes its use for a ballot polling audit using details of the 2020 US Presidential election in the state of Virginia. Our conclusions, the availability of an audit implementation and acknowledgements may be found in sections \ref{sec:conc}, \ref{sec:avail} and \ref{sec:ack} respectively.

>>>>

A tabulation audit will either end with a declaration that an election outcome is correct, or escalate to a full hand count. The integrity of an audit may be judged by how it deals with incorrect outcomes. A {\em risk-limiting audit (RLA)} guarantees a minimum probability that it will perform as it is supposed to (escalate to a full hand count) if the outcome is incorrect. Equivalently, this is also a guarantee limiting the probability of audit error when the outcome is incorrect. The {\em risk limit} of an RLA is the (guaranteed) maximum probability that an incorrect election outcome would be declared correct (and not proceed to a full hand count). Lower risk limits are better.

@@

\subsection{Background on RLAs}
All RLAs sample one or more ballots at random; we will refer to each such set of ballots as a {\em round}. The ballots are manually examined, and a stopping condition computed, which determines whether (a) the audit ends in success (the election outcome is declared correct) or (b) another round should be drawn (more information is needed before a determination). In principle, the stopping condition could indicate a third option too: (c) the audit proceeds to a full manual hand count. However, a manual hand count presents significant logistical challenges, and there is always a chance that it will have been unnecessary, hence (c) is generally not incorporated. Election officials would typically decide to perform a full manual hand count if the audit does not stop in spite of drawing a large number of ballots, typically over multiple rounds. They would be influenced by the certification deadline, the estimated number of human hours required for another round, the logistical costs of a full hand count, and the impact of any decision on citizen confidence.

There are three types of RLAs: ballot comparison RLAs, batch comparison RLAs and ballot polling RLAs. This paper focuses on ballot polling RLAs which have been used in a number of US state pilots (California, Georgia, Indiana, Michigan, Ohio, Pennsylvania, Virginia and elsewhere) and in real statewide audits (Georgia, Virgina) \cite{vv_audits} as well as in audits of smaller jurisdictions, such as Montgomery County, Ohio \cite{usenix_minerva}. Ballot and batch comparison RLAs are described in \ref{sec:related}.

\subsection{Ballot Polling RLAs}
\label{sec:polling}
Ballot and batch comparison RLAs compare information gathered through manual examination of the sampled ballots with the corresponding information claimed by the voting system. For example, the information could be the vote on a particular ballot (stored by the voting system as a CVR or Cast Vote Record) or the tally of a particular box of ballots. A ballot polling RLA \cite{RLA}, on the other hand, simply tallies the sampled ballots. It requires a much larger number of ballots than a ballot comparison RLA, but tends to be more feasible because it does not require any additional functionality of the voting system; in particular it does not require the system to generate or provide CVRs. What is needed is a complete ballot manifest (a list of ballot storage containers and the number of ballots in each) which enables the creation of a well defined list of the ballots and their locations (the fifth ballot in box number 20, for example).

Ballot polling audits proceed as follows. 
\begin{enumerate}
\item A first round \cite{usenix_minerva} size---the number of ballots sampled before first checking the stopping condition---is chosen. 
\item Ballots on the ballot manifest are sampled uniformly at random using a pseudorandom number generator typically seeded by a natural source of randomness like rolling dice.
\item The physical ballots are found and manually interpreted, recording the manual interpretations. 
\item Based on the manual interpretations, the stopping condition is computed. 
\item If more ballots are to be drawn, the next round size is chosen. Round sizes, including the first one, may be computed based on a desired probability of audit completion at the end of the round, and may take into consideration loose estimates of the resources required. For RLAs required by statute or law, certification deadlines would play a large role, as the audit would need to be completed before the deadline. 
\end{enumerate}

@@

Election officials typically draw ballots in large round sizes:  see for example \cite{va-2022,RI-report}. Note also that, in addition to allowing users to directly enter a round size or choose the expected number of ballots drawn by \BRAVO, Arlo provides choices of stopping probabilities of $0.9$, $0.8$ and $0.7$ (\cite{usenix_minerva} provides estimates of these round sizes for each state in the 2020 US Presidential election, for a $0.9$ probability of stopping). Further, at both audits we attended, election officials chose stopping probabilities of $0.9$ and we are not aware of any ballot polling RLA performed on ballots cast in a governmental election that drew ballots one at a time (though the stopping condition can be computed one ballot at a time, the ballots are drawn in rounds). \BRAVO hence cannot be used as a B2 audit in these scenarios.

@@

\subsection{Adversarial Model for RLAs}
Detailed descriptions of best practices for post-election audits may be found in \cite{best-practices,why-and-how}. For our purposes, we will assume that the best practices are followed: the paper trail consists of hand-marked paper ballots and is secured; a public compliance audit is carried out before the RLA to ensure that the processes for securing the paper trail were followed; voter authentication and registration processes are verified, and only legitimate voters cast no more than a single vote each; the risk-limiting audit is public. We will further assume that all software used in the RLA is open source and well-defined, so its output may be reproduced and thus verified by an observer wishing to do so with their own software.

Referring to the ballot polling audit steps described in section \ref{sec:polling} above, we further assume that a secure PRNG is used; the seed is generated uniformly at random in a public process; the process of locating ballots is publicly observable and the located ballots can be viewed by the public. Because the PRNG is well-defined, as is the stopping condition, we may assume that the stopping condition is correctly computed, because it can be checked by the public through knowledge of the seed and the drawn ballots. Thus the only variable is round size.

We define a {\em weak adversary} as one who can choose the first and subsequent round sizes before the audit begins and a {\em strong adversary} as one who can choose any round size at any time before the round begins.

\subsection{Open Questions}
Zag\'{o}rski {\em et al.} propose ballot polling RLA \Minerva \cite{usenix_minerva}, which does not need ballot order and relies only on sample and round tallies. They prove that it is risk-limiting when the number of relevant ballots drawn in each round is pre-determined before any ballots are examined; that is, for a weak adversary. They do not address the case of a strong adversary (such as an audit insider) who can determine the size of the next round after knowing what votes are on the ballots sampled thus far. In particular, an open question about \Minerva is whether the computation of a risk limit assuming a weak adversary applies to an attack by a strong adversary, or is the risk limit computation incorrect when the adversary is strong? Can the strong adversary increase the audit's error probability beyond its declared risk limit? Or is there no probabilistic adversarial advantage to being able to compute next round sizes after knowing the drawn sample? We do not answer this question, and to our knowledge, it remains open.

@@

A major limitation of our understanding of the ballot polling problem as a community is that we use the number of ballots drawn or values proportional to this number \cite{mclaughlin_thesis,bernhard-diss,RI-report} as measures of the workload of an audit. If this were a correct measure of the workload of an audit, we would want to use B2 audits (round size is one) and make decisions about stopping the audit after drawing each ballot, because this leads to the smallest expected number of ballots. As described above, election officials, on the other hand, greatly prefer drawing many ballots at once. From conversations with election officials and staff members of Verified Voting, Brennan Center and Common Cause who have been training election officials to perform RLAs, we estimate that this preference is likely due to the following. 
\begin{description}
\item Firstly, each round has an overhead workload as well, including setting up the round and communicating among the various localities involved in conducting the audit (for example, audits of statewide contests involve the drawing of ballots at county offices where the ballots are stored). 
\item Secondly, there is an overhead to finding a storage box and unsealing it. For large round sizes, multiple ballots may be drawn at once from a box, and the number of boxes retrieved is smaller than the number of ballots (storage boxes commonly contain many hundreds of ballots each). For smaller round sizes, the number of times a box is retrieved would be roughly identical to the number of ballots drawn, as it is unlikely that a single box will hold multiple ballots from the sample. 
\item Finally, in the current environment of misinformation, election officials fear a misleading audit sample (falsely indicating that the loser won), preferring to structure audits to reduce the chances of such samples, thus implicitly choosing larger round sizes. 
\end{description}
Thus the workload of an audit is not simply a linear (or affine) function of the number of ballots drawn. Relatedly, an optimal round schedule is not completely determined by the expected number of ballots drawn. It depends on other variables as well. The consideration of all these variables is necessary while planning an audit.

\subsection{Our Contributions}
Our primary contribution is a new RLA, \Providence, which gives the efficiency of \Minerva and is also resistant to a strong adversary. The stopping condition for \Minerva does not take into account the sample obtained in previous rounds, and, in \cite{usenix_minerva}, its risk limit is estimated through weighted averages across multiple rounds, assuming that round sizes do not depend on the previous sample. We are able to derive a new stopping condition for which a far simpler proof of the risk-limiting property is possible. In particular, this proof does not require an assumption about round sizes.

We provide the following:
\begin{enumerate}
\item Proof that \Providence is an RLA and resistant to a strong adversary.
\item Simulations of \Providence, \Minerva, SO \BRAVO, and EoR \BRAVO which show that \Providence uses number of ballots similar to those of \Minerva, both fewer than either version of \BRAVO.
\item Results and analysis from the use of \Providence in a pilot audit in Rhode Island.
\item A model of workload that includes the overhead effort of each round and the overhead effort of retrieving a storage unit of ballots; simulations that illustrate the use of this model to compare the different types of ballot polling audits and to plan an audit with minimal workload.
\item An analysis of round size as a function of the maximum acceptable probability of a misleading audit sample.
\item Open source implementation of \Providence and audit planning tools. 
%including the novel metric Probability of Misleading(name?)
\end{enumerate}

@@

\subsection{Organization} 
Sections \ref{sec:model} and \ref{sec:related} provide background, describing the audit model and related work respectively. Section \ref{sec:prov} describes the \Providence audit, Section \ref{sec:sims} the simulations comparing the number of ballots drawn using various ballot polling audits and section \ref{sec:pilot} the use of \Providence in an audit carried out by the Board of Elections of Rhode Island. Section \ref{sec:workload} presents our workload model and describes its use for a ballot polling audit using details of the 2020 US Presidential election in the state of Virginia. Our conclusions, the availability of an audit implementation and acknowledgements may be found in sections \ref{sec:conc}, \ref{sec:avail} and \ref{sec:ack} respectively.

### 2023-02-12 providence/sections/model.tex
added model. worked more on intro.

%Related Work
Bernhard provides a good description of the RLA and its assumptions, and also describes the process on the ground \cite{bernhard-sok}.

The \BRAVO audit \cite{bravo} is the most popular ballot polling audit. When ballots are sampled one at a time, it is the audit with the smallest expected number of ballots drawn.

The \Minerva audit \cite{usenix_minerva,arxiv_athena} was developed for use with large first round sizes, and has been proven to be risk limiting when the round schedule for the audit is fixed before any ballots are drawn. First-round sizes for a stopping probability of $0.9$ when the announced tally is correct have been shown to be smaller than those for EoR and SO \BRAVO for a wide range of margins; simulations \cite{arxiv_athena} support these observations. Additional simulations \cite{simulations} have shown that \Minerva requires fewer ballots than EoR and SO \BRAVO over multiple rounds and for smaller stopping probability. As expected, the advantage of \Minerva decreases for smaller stopping probability (smaller round sizes) as such round schedules approach the B2 round schedule (1,1,1,\ldots) for which \BRAVO is known to be most efficient.

Ballot polling audit simulations provide a means of educating the public and election officials \cite{dice} and to understand audit properties \cite{mclaughlin_thesis,simulations_house, blom_IRV, DBLP:conf/evoteid/HuangRSTV20}. There is work measuring the amount of time taken to examine a single ballot \cite{RI-report}. 
Simple workload estimates may be obtained by using the number of ballots drawn \cite{bernoulli-ballot-polling}, a more thorough workload estimation model includes the time taken to access individual ballots\cite{bernhard-diss}.

@@

The stopping conditions of \BRAVO and \Minerva rely on the following ratios.

\begin{definition}[\BRAVO Ratio] \label{def:bravo-ratio} The \BRAVO audit uses the ratio $\sigma$. Consider a sample size of $n$ ballots with $k$ for the reported winner. The proportion of ballots for the reported winner under the alternative hypothesis and null hypothesis are $p_a$ and $p_0$ respectively.
\begin{equation}
    \sigma(k, p_a, p_0, n) \triangleq \frac{p_a^{k} (1-p_a)^{n-k}}{p_0^{k} (1-p_0)^{n-k}} 
    \label{eqn:bravoratio}
\end{equation}
\end{definition}

In \BRAVO, $p_0=\frac{1}{2}$. A \BRAVO audit outputs correct if and only if
$$\sigma(k,p_a,\frac{1}{2},n)\ge \frac{1}{\alpha}.$$

%If testing the \BRAVO stopping condition after each individual ballot
% is drawn (a \B \BRAVO audit), 
If $K$ is the random variable indicating the number of ballots in the sample that contain a vote for the reported winner, it is easy to see that the ratio $\sigma$ is the likelihood ratio:
$$
\frac{Pr[K=k|H_a,n]}{Pr[K=k|H_0,n]}= \frac{\binom{n}{k}p_a^{k} (1-p_a)^{n-k}}{\binom{n}{k}(\frac{1}{2})^n} =\sigma(k, p_a, \frac{1}{2}, n)
$$

\begin{comment}
\begin{definition}[$(\alpha,p)$-\BRAVO ]\label{def:bravo}  An audit $\mathcal{A}$ is the \B~$(\alpha, p)$-\BRAVO audit iff the following stopping condition is tested at each ballot draw. If the sample $X$ is of size $n$ and has $k$ ballots for the winner,  
\begin{equation}
    \mathcal{A}(X) =  \left\{ \begin{array}{ll} \text{Correct} & ~\sigma(k, p, \frac{1}{2}, n) 
         %\triangleq \frac{p^{k} (1-p)^{n-k}}{(\frac{1}{2})^n} 
        \geq \frac{1}{\alpha}\\
        Undetermined & ~else 
    \end{array}
    \right .
    \label{eqn:bravo}
\end{equation}
\end{definition}
\end{comment}

\BRAVO is an instance of Wald's Sequential Probability Ratio Test (SPRT) \cite{wald}. In the more general SPRT, the test can also reject the alternative hypothesis, and there is an additional parameter $\beta$, the probability of incorrectly rejecting the alternative hypothesis. In an RLA, this corresponds to the audit having a third output: \emph{proceed to a full manual count of the ballots}. In the existing literature, ballot polling audits do not include this possibility (i.e. they set $\beta=0$) in order to give maximum flexibility to election officials in choosing when to proceed to a full manual count.

Where \BRAVO uses the ratio of the values of the probability distribution functions, \Minerva uses the ratio of their \emph{tails}. Now it becomes useful to have shorthand for a sequence of cumulative round sizes and the corresponding sequence
of cumulative winner ballot tallies.
We use:
$$\bm{n_j}\triangleq(n_1,n_2,\ldots,n_j) \quad\text{and}\quad \bm{k_j}\triangleq(k_1,k_2,\ldots,k_j)$$
Also, let $K_j$ be the random variable indicating the cumulative number of ballots in the sample after the $j$th round is drawn.

\begin{definition}[\Minerva Ratio] \label{def:minerva_ratio} The \R \Minerva audit uses the ratio $\tau_j$. We use cumulative round sizes $\bm{n_j}$, with corresponding $\bm{k_j}$ ballots for the reported winner in each round. The proportion of ballots for the reported winner under the alternative hypothesis and null hypothesis are $p_a$ and $p_0$ respectively.
         \begin{equation}
         \begin{aligned}
             \label{eqn:tau}
                 \tau_{j}(k_{j}, p_a,p_0, \bm{n_j}, \alpha )  \triangleq\\
                 \frac{Pr[K_{j} \geq k_{j} \wedge \forall_{i < j} ({\mathcal{A}}(X_i) ~\neq \text{Correct}) \mid H_a, \bm{n_j}]}{Pr[K_{j} \geq k_{j} \wedge \forall_{i < j} ({\mathcal{A}}(X_i) ~\neq \text{Correct}) \mid H_0, \bm{n_j}]}
         \end{aligned}
         \end{equation}
\end{definition}

\begin{comment}
\begin{definition}[$ (\alpha, p, \bm{n_j} ) $-\Minerva]
     \label{def:minerva}
     Given \B $(\alpha, p)$-\BRAVO and cumulative round sizes\\ $\bm{n_j}$, the corresponding \R \Minerva stopping rule for the $j^{th}$ round is:
 \begin{equation}
     \mathcal{A}(X_{j})=  \left\{ \begin{array}{ll} \text{Correct} ~~~~ \tau_{j}(k_{j}, p_a, \frac{1}{2}, \bm{n_j}, \alpha ) \geq \frac{1}{\alpha}\\
             % & \\
             % incorrect& ~~~ \sigma_n < \frac{\beta}{1-\alpha} \\
             % & \\
             Undetermined ~~else \\
         \end{array}
         \right .
         \label{eqn:minerva-test}
 \end{equation}
\end{definition}
\end{comment}

In this work, we consider ballot polling RLAs only and thus compare \Providence with \BRAVO and \Minerva.

>>>>

% Model

@@
